On the performance of the MAC model

### 2018-10-29 2018_nips_vigil/smac.tex
S-mac with both equations side-by-side

\subsection*{Control Unit}

\begin{align*}
	&q_i = U_i^{[d \times 2d]} q + b_i^{[d]}  \tag{c0} \\
	\cline{1-2}
	&cq_i = W_{\textsf{cq}}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
	&ca_{is} = W_{\textsf{ca}}^{[1 \times d]} (cq_i \odot \mathbf{cw}_s)  \tag{c2.1}\\
	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
	&\mathbf{c}_i = \sum_s cv_{is} \, \mathbf{cw}_s  \tag{c2.3}
\end{align*}
Only eqn.~(c0) above is \emph{position dependent}

\subsection*{Read Unit}

\begin{align*}
	&\mathbf{\tk}_{hw} = U_{\textsf{proj}}^{[d \times d]} \mathbf{k}_{hw} + b_{\textsf{proj}}^{[d]} \tag{r0} \\
	\cline{1-2}
	&I_{ihw} = \mathbf{m}_{i-1} \odot \mathbf{\tk}_{hw} \tag{r1} \\
	&I'_{ihw} = \mathbf{\tk}_{hw}  + W_{\textsf{I}}^{[d \times d]} I_{ihw} + b_{\textsf{I}}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{\textsf{ra}}^{[1 \times d]} (\mathbf{c}_i \odot I'_{ihw})  \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\mathbf{r}_i = \sum_s rv_{ihw} \, \mathbf{\tk}_{hw}  \tag{r3.3}
\end{align*}

Note that $\mathbf{\tk}_{hw}$ can be \emph{precomputed} before the reasoning steps.

\subsection*{Write Unit}

\begin{equation}
\mathbf{m}_i = W_{\textsf{m}}^{[d \times d]} \mathbf{r}_i + b_{\textsf{m}}^{[d]} \tag{w1}
\end{equation}

>>>>

In the description below, the original MAC cell equations are shown on the \emph{left}
while our simplified equations are shown on the \emph{right}.
(The equation numbering is the same as in~\cite{hudsonManning18}.)

\setlength{\columnsep}{1cm}
\setlength{\columnseprule}{0.5pt}
%\def\columnseprulecolor{\color{blue}}

\subsection*{Control Unit:}
\newcommand{\cq}{cq}
\newcommand{\ca}{ca}
\newcommand{\cw}{\mathbf{cw}}
\newcommand{\cc}{\mathbf{c}}

\begin{multicols}{2}
	\noindent
	\begin{align*}
	&q_i = U_i^{[d \times 2d]} q + b_i^{[d]}  \tag{c0} \\
	\cline{1-2} \\[2pt]
	&cq_i = W_{\cq}^{[d \times 2d]} [c_{i-1}, q_i] + b_{\cq}^{[d]}  \tag{c1} \\
	&ca_{is} = W_{\ca}^{[1 \times d]} (cq_i \odot \cw_s) + b_{\ca}^{[1]}
	\tag{c2.1}\\
	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
	&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
	\end{align*} 
	\columnbreak
	\begin{align*}
	&q_i = U_i^{[d \times 2d]} q + b_i^{[d]}  \tag{c0} \\
	\cline{1-2} \\[2pt]
	&cq_i = W_{\cq}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
	&ca_{is} = W_{\ca}^{[1 \times d]} (cq_i \odot \cw_s)  \tag{c2.1}\\
	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
	&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
    \end{align*} 
\end{multicols}

Above, $i$ refers to index/position of the reasoning step. Note that the weights/biases
are \emph{shared} across reasoning steps except for eqn.~(c0) above, which 
is \emph{position-aware}~\cite{hudsonManning18}, i.e. depends
on $i$.

\subsection*{Read and Write Unit:}
\newcommand{\kb}{\mathbf{k}}
\newcommand{\tkb}{\mathbf{\hat{k}}}
\newcommand{\mi}{\textsf{I}}
\newcommand{\mpi}{\textsf{I'}}
\newcommand{\mem}{\mathbf{m}}
\newcommand{\rr}{\mathbf{r}}

\begin{multicols}{2}
	\noindent
	\begin{align*}
	\\
	\cline{1-2}
	&I_{ihw} = (W_{m}^{[d \times d]} m_{i-1} + b_{m}^{[d]}) \\
	           & \qquad \quad \odot (W_{k}^{[d \times d]} k_{i-1} + b_{m}^{[d]}) \tag{r1} \\
	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{m}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{m}^{[d]} \tag{w1}	
	\end{align*}
	\columnbreak
	\begin{align*}
	&\tkb_{hw} = U_{\textsf{proj}}^{[d \times d]} \mathbf{k}_{hw} + b_{\textsf{proj}}^{[d]} \tag{r0} \\
	\cline{1-2}
	&I_{ihw} = \mem_{i-1} \odot \tkb_{hw} \tag{r1} \\ \\
	&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \tkb_{hw} \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \tkb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{m}^{[d \times d]} \rr_i + b_{m}^{[d]} \tag{w1}
	\end{align*}
\end{multicols}

Note that $\tkb_{hw}$ can be \emph{precomputed} before the reasoning steps.
